%!TEX root = foglio.tex

% =================================================

\section{Diffusion/Elliptic Problems}

% =================================================

\textbf{Weak Formulation.} Given $V$, $F:V\to\RR$ functional and $a:V\times V\to\RR$ bilinear form,
\begin{equation*}
\boxed{\text{find } u\in V\ :\ a(u,v)=F(v)\quad\forall v\in V}\qquad\quad
\end{equation*}

\smallskip

\textbf{Lax-Milgram Lemma.} Assume that:
\begin{enumerate}
\item $V$ Hilbert space with $\norm{\cdot}_V$ and $\sca{\cdot,\cdot}$
\item $F\in V'$, i.e. $\abs{F(v)}\leq \norm{F}_{V'}\norm{v}_V$
\item $a$ cont., i.e. $\abs{a(u,v)}\leq M \norm{u}_V\norm{v}_V$
\item $a$ coercive, i.e. $a(v,v)\geq \alpha \norm{v}_V^2$
\end{enumerate}
Then: $\exists\,!\ u$ sol. di WF, and $\norm{u}_V\leq \nicefrac{\norm{F}_{V'}}{\alpha}$

\medskip

\textbf{Galerkin Approximation.} If you can build $V_h\subset V$ s.t. $\text{dim }V_h=N_h<\infty$ ($\Rightarrow$ $V_h$ closed subspace), then WF becomes G:
\begin{equation*}
\boxed{\text{find } u_h\in V_h\ :\ a(u_h,v_h)=F(v_h)\quad\forall v_h\in V_h}\qquad
\end{equation*}

\begin{itemize}
\item \emph{well-posedness} follows from LM
\item \emph{stability} is the continuous dependence from data in LM
\item \emph{consistency} $\equiv$ \textbf{Galerkin Orthog.} GO:
\begin{equation*}
a(u-u_h,v_h)=0\qquad\forall v_h\in V_h
\end{equation*}
\item if we assume \textbf{space saturation}
\begin{equation*}
\lim_{h\to 0}\inf_{v_h\in V_h}\norm{v-v_h}_V=0\quad\forall v\in V
\end{equation*}
then \emph{convergence} $\equiv$ \textbf{Céa Lemma}:
\begin{equation*}
\norm{u-u_h}_V\leq \frac{M}{\alpha}\,\inf_{v_h\in V_h}\norm{u-v_h}_V
\end{equation*}
\begin{proof}
See whiteboards.
\end{proof}
\end{itemize}

Last but not least: Problem G is equivalent to the following linear system LS of equations:
\begin{equation*}
\boxed{\text{find } \uv\in\RR^{N_h}\ :\ A\uv=\Fv}\qquad\qquad
\end{equation*}
where $A\in\RR^{N_h\times N_h},\ \Fv\in\RR^{N_h}$.

\begin{proof}
See whiteboards.
\end{proof}

Moral of the story: $V_h$ must be chosen to ensure the saturation assumption and the computation of the integrals $A_{ij}=a(\phi_j,\phi_i)$ and $F_i=F(\phi_i)$.

\medskip

\textbf{The Finite Element Method.} We consider a domain $\Omega$ with polygonal shape (we do not take into account error due to the approximation of a non-polygonal domain with a FE grid). A \textbf{mesh} is a finite cover of $K$ non-overlapping triangles, also called \emph{triangulation}: $\Tc=\bigcup K$. Actually: in 1D, intervals; in 2D, triangles but we'll see also quadrilaterals; in 3D, tetrahedra but we'll see also hexahedra.






